A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-04-29 paper.tex
Added a missing reference to the related work

Synthesis of safety games is a thoroughly explored area of research with most
efforts directed toward solving games with BDDs \cite{burch1990} and abstract
interpretation \cite{walker2014,brenguier2014}. Satisfiability solving has been used
previously for synthesis in a suite of methods proposed by Bloem et al.
\cite{bloem2014}. The authors propose employing competing SAT solvers
to learn clauses, which is similar to our approach but does not unroll the
game. They also suggest QBF solver, template-based, and Effectively
Propositional Logic (EPR) approaches.

@@

Incremental induction \cite{bradley2011} is another technique for unbounded
model checking with an equivalent synthesis method \cite{morgenstern2013},
which computes sets of states that overapproximate the losing states (similar
to our $B^m$) and another set of winning states (similar to the negation of
$B^M$). Their algorithm maintains a similar invariant over the sets of losing
states as our approach and has the same termination condition. It differs in
how the sets are computed, which it does by inductively proving the number of
game rounds required by the environment to win from the initial state.

>>>>

Synthesis of safety games is a thoroughly explored area of research with most
efforts directed toward solving games with BDDs \cite{burch1990} and abstract
interpretation \cite{walker2014,brenguier2014}. Satisfiability solving has been used
previously for synthesis in a suite of methods proposed by Bloem et al.
\cite{bloem2014}. The authors propose employing competing SAT solvers to learn
clauses representing bad states, which is similar to our approach but does not
unroll the game.  They also suggest QBF solver, template-based, and Effectively
Propositional Logic (EPR) approaches.

@@

Incremental induction \cite{bradley2011} is another technique for unbounded
model checking that inspired several approaches to synthesis including the work
presented here.  Morgenstern et al.~\cite{morgenstern2013} proposed an
technique that computes sets of states that overapproximate the losing states
(similar to our $B^m$) and another set of winning states (similar to the
negation of $B^M$).  Their algorithm maintains a similar invariant over the
sets of losing states as our approach and has the same termination condition.
It differs in how the sets are computed, which it does by inductively proving
the number of game rounds required by the environment to win from a state.
Chiang and Jiang~\cite{Chiang2015} recently proposed a similar approach that
focusses on computing the winning region for the controller forwards from the
initial state in order to take advantage of reachability information and bad
transition learning without needing to discard learnt clauses.
